### 2018-04-28 paper/security-analysis.tex
Adds things to cover in security analysis

>>>>

The message \(m\) remains the same from hop to hop during the onion routing, 
hence a global observer can track the message through the network.

We can choose different properties for \(\Enc*\).
What makes sense is to choose an authenticated encryption 
scheme~\cite{AuthEncryption}.
We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, \eg 
the one by \textcite{OTPKX} which is both deniable and authenticated and 
provides \ac{DEN-SS}.
